Refinements for Open Automata

### 2023-06-20 2021-Refinement/paper/refinementarticleV2.tex
relectire

The refinement concept also plays  an important role in software engineering. In addition to helping to cope with the complexity \LUDO{of what?}, refinement provides a foundation for ensuring  system (software) correctness. The correctness of a system can
be established by proving, that a system refines its specification.
%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification. The refined model features all the specified behaviours with more concrete details. From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}. Each \LUDO{each what?} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation. This definition \LUDO{which definition?}, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.

@@

The origins of the simulation are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.  Many work  contributed to the  development of the refinement calculus \LUDO{TODO: define refinement calculus} in various area (e.g. \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}). However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,

>>>>

The refinement concept also plays  an important role in software engineering. In addition to helping to cope with the complexity of requirements and design \LUDO{\st{of what?}}, refinement provides a foundation for ensuring  system (software) correctness. The correctness of a system can
be established by proving, that a system refines its specification.
%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification. The refined model features all the specified behaviours with more concrete details. From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}. Each semantic treatment \LUDO{\st{each what?}} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation. This refinement semantics is  used to study the behaviour of  closed
systems \LUDO{\st{which definition?}}, i.e.  systems whose behaviour is fully defined. It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.

@@

The origins of the simulation are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.  Many work  contributed to the  development of the refinement calculus \LUDO{TODO: define refinement calculus} in various area (e.g. \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
\RAB{This development approach is primarily concerned with  whether a program is correct with respect to given properties, and how to improve (refine) a program while preserving its correctness.}
 However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,
